Headgroup Structure and Cation Binding in Phosphatidylserine Lipid Bilayers

### 2019-09-11 Manuscript/manuscriptPS.tex
MD simulations

lipid/counter-ions  & force field & \footnote{Number of lipid molecules}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analyses}t$_{{\rm anal}}$ (ns)  & \footnote{Number of reference for simulation files}files & \tabularnewline

@@

The C--H bond order parameters were calculated directly
from the carbon and hydrogen positions using the definition
\begin{equation}
S_{\rm CH}=\frac{1}{2}\langle 3\cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the C--H bond and the membrane normal
(taken to align with $z$, with bilayer periodicity in the $xy$-plane).
Angular brackets denote average over all sampled configurations.
The order parameters were calculated by first averaging over time separately
for each lipid in the system, and then calculating the average and
the standard error of the mean over the different lipids. The analysis can be conducted using a
Python program ({\tt calcOrderParameters.py}, available in Ref.~\citenum{MATCHgit}) that uses the
MDAnalysis library \cite{agrawal11,gowers16}.
For united atom models, the positions of hydrogens were generated before the order parameter calculation using the {\tt protonate} tool
of the Gromacs 3 sofware package \cite{gromacsMANUAL}.
The ion number density profiles were calculated using the {\tt gmx density} tool
of the Gromacs sofware package \cite{gromacsMANUAL}.

>>>>

lipid/counter-ion & force field & \footnote{Number of lipid molecules}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analyses}t$_{{\rm anal}}$ (ns)  & \footnote{Number of reference for simulation files}files & \tabularnewline

@@

The C--H bond order parameters were calculated directly
from the carbon and hydrogen positions using the definition
\begin{equation}
S_{\rm CH}=\frac{1}{2}\langle 3\cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the C--H bond and the membrane normal
(taken to align with $z$, with membrane in the $xy$-plane).
Angular brackets denote average over all sampled configurations.
The order parameters were calculated by first averaging over time separately
for each lipid in the system, and then calculating the average and
the standard error of the mean over the different lipids. The analysis can be conducted using the
Python program {\tt calcOrderParameters.py}, available in Ref.~\citenum{MATCHgit}, that uses the
MDAnalysis library \cite{agrawal11,gowers16}.
For the united atom force fields, the positions of hydrogens were generated before the order parameter calculation using the {\tt protonate} tool
of the Gromacs 3 sofware package \cite{gromacsMANUAL}.
The ion number density profiles were calculated using the {\tt gmx density} tool
of the Gromacs sofware package \cite{gromacsMANUAL}.
